### 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
update files

    %Folio
    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 83\end{tabular}}}}%

    \put(0.10902655,0.55515604){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 11\end{tabular}}}}%
    \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%

@@

    %Finalizacion
    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%

>>>>

    %Folio
    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 113\end{tabular}}}}%

    \put(0.10902655,0.55515604){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 11\end{tabular}}}}%
    \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%

@@

    %Finalizacion
    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdfsdf\end{tabular}}}}%
    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
